---
title: "Analyze Finanical Report Data Template"
author: "Jason Wang"
date: '`r Sys.Date()`'
output:
  html_document:
    number_sections: yes
    df_print: paged
    theme: cosmo
    toc: yes
    toc_depth: 2
params:
    id_stock: "002460"
    date_report: "2017-12-31"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = F, fig.width=10, fig.align = 'center', comment=NA, autodep=T, echo = FALSE)
#rm(list=ls())
library(DBI)
source("./CODE/LIB/lib_generic.R")
source("./CODE/LIB/lib_analy_finan_data.R")
```



```{r import_data, include=FALSE}
########## overall 
num_qtr_back <- 8
nam_var_date <- "F001D"
nam_var_id_stock <- "SECCODE"
nam_var_key <- c(nam_var_date, nam_var_id_stock)
nam_var_op_income <- "PNL_F006N"
nam_var_op_cost <- "PNL_F007N"
nam_var_net_profit <- "PNL_F027N"
nam_var_gross_profit <- "PNL_gross_profit"
nam_var_net_op_cash <- "CF_F015N"
nam_var_inventory <- "BAL_F015N"
nam_var_advance_receipt <- "BAL_F043N"
nam_var_interest_loan <- c("BAL_F039N", "BAL_F050N", "BAL_F053N", "BAL_F054N")
###################### source data #######################
## FIXED DB connection
conn_db <- dbConnect(RSQLite::SQLite(), paste0("./DATA/CLEAN/", "db_finan_report.sqlite"))
## collect metadata
meta_bal <- as_tibble(dbReadTable(conn_db, "meta_ts_bal_sheet"))
meta_pnl <- as_tibble(dbReadTable(conn_db, "meta_ts_income_stat"))
meta_cash <- as_tibble(dbReadTable(conn_db, "meta_ts_cash_flow"))
# checks assumption of prime key!
stopifnot(identical(sort(nam_var_key), sort(meta_bal$varR[meta_bal$prime_key == 1])))
stopifnot(identical(sort(nam_var_key), sort(meta_pnl$varR[meta_pnl$prime_key == 1])))
stopifnot(identical(sort(nam_var_key), sort(meta_cash$varR[meta_cash$prime_key == 1])))
## balance sheet collected: 
df_bal_cuml <- dbGetQuery(conn_db, paste0("SELECT * FROM ", "tabl_ts_bal_sheet", 
                                          " WHERE SECCODE = '", params$id_stock, "'")) %>% 
  as_tibble() %>% 
  arrange_(.dots = nam_var_date)
## income statement collected: 
df_pnl_cuml <- dbGetQuery(conn_db, paste0("SELECT * FROM ", "tabl_ts_income_stat", 
                                          " WHERE SECCODE = '", params$id_stock, "'")) %>% 
  as_tibble() %>% 
  arrange_(.dots = nam_var_date)
## cash flow collected: 
df_cash_cuml <- dbGetQuery(conn_db, paste0("SELECT * FROM ", "tabl_ts_cash_flow", 
                                          " WHERE SECCODE = '", params$id_stock, "'")) %>% 
  as_tibble() %>% 
  arrange_(.dots = nam_var_date)
############################################## source data  ###
### checks
stopifnot(identical(sort(names(df_bal_cuml)), sort(meta_bal$varR)))
stopifnot(identical(sort(names(df_cash_cuml)), sort(meta_cash$varR)))
stopifnot(identical(sort(names(df_pnl_cuml)), sort(meta_pnl$varR)))
### combine B/S, PnL and cash flow
meta_ts_fin_cuml <- meta_bal %>% 
  bind_rows(filter(meta_cash, grepl("CF_", varR))) %>% 
  bind_rows(filter(meta_pnl, grepl("PNL_", varR)))
df_ts_fin_cuml <- df_bal_cuml %>% 
  left_join(select(df_pnl_cuml, one_of(nam_var_key), starts_with("PNL_")), by = nam_var_key) %>% 
  left_join(select(df_cash_cuml, one_of(nam_var_key), starts_with("CF_")), by = nam_var_key) %>% 
  mutate_at(meta_ts_fin_cuml$varR[toupper(meta_ts_fin_cuml$type) == "NUM"],
            function(x) if_else(is.na(x), 0, x)) %>% 
  mutate_(.dots = set_names(paste(nam_var_op_income, " - ", nam_var_op_cost), "PNL_gross_profit"))
meta_ts_fin_cuml <- bind_rows(
  meta_ts_fin_cuml, 
  data_frame(varR = "PNL_gross_profit", label_en = "Gross Profit", type = "num"))
stopifnot(all(!duplicated(meta_ts_fin_cuml$varR)))
stopifnot(identical(sort(names(df_ts_fin_cuml)), sort(meta_ts_fin_cuml$varR)))
### get single qtr information
# note special treatment must be applied as 1st quarter is always starting point
df_ts_fin_single <- get_increment_from_cumulate(df_ts_fin_cuml, nam_var_date) %>% 
  filter_(.dots = paste0("!grepl('-03-31', ", nam_var_date, ")")) %>% 
  bind_rows(filter_(df_ts_fin_cuml, .dots = paste0("grepl('-03-31', ", nam_var_date, ")"))) %>% 
  arrange_(.dots = nam_var_date)
### get last defined qtr back
tmp_date_sel <- min(max(pull(df_ts_fin_cuml, nam_var_date)), as.character(params$date_report))
date_qtr_back <- seq(as.Date(tmp_date_sel) + 1,
                   length.out=as.numeric(num_qtr_back) , by='-1 quarter') - 1 
date_qtr_back <- sort(as.character(date_qtr_back))
```



# Overview {.tabset}

We examine stock **`r params$id_stock`** based on the financial report at per **`r tmp_date_sel`**.

## Cumulative YtD view

```{r warning = FALSE}
nam_var_2_plot <- c(nam_var_op_income, nam_var_net_profit, nam_var_net_op_cash)
lst_res_2_show <- select(df_ts_fin_cuml, one_of(nam_var_date, nam_var_2_plot)) %>% 
  arrange_(.dots = nam_var_date) %>% 
  cal_QoQ_YoY_of_df(nam_var_2_plot) %>% 
  filter_(.dots = paste0(nam_var_date, " %in% date_qtr_back")) %>% 
  plot_df_val_QoQ_YoY(rename(select(meta_ts_fin_cuml, varR, label_en), label = label_en), nam_var_date)
plotly::ggplotly(lst_res_2_show$obj_ggplot)
```

```{r}
DT::datatable(lst_res_2_show$df_view_ts, extensions = 'FixedColumns', options = list(
  pageLength = 3,
  scrollX = TRUE,
  searchHighlight = TRUE,
  fixedColumns = list(leftColumns = 1)), rownames = FALSE)
```

## Single Qtr 

```{r}
nam_var_2_plot <- c(nam_var_op_income, nam_var_net_profit, nam_var_net_op_cash)
lst_res_2_show <- select(df_ts_fin_single, one_of(nam_var_date, nam_var_2_plot)) %>% 
  arrange_(.dots = nam_var_date) %>% 
  cal_QoQ_YoY_of_df(nam_var_2_plot) %>% 
  filter_(.dots = paste0(nam_var_date, " %in% date_qtr_back")) %>% 
  plot_df_val_QoQ_YoY(rename(select(meta_ts_fin_cuml, varR, label_en), label = label_en), nam_var_date)
plotly::ggplotly(lst_res_2_show$obj_ggplot)
```

```{r warning = FALSE}
DT::datatable(lst_res_2_show$df_view_ts, extensions = 'FixedColumns', options = list(
  pageLength = 3,
  scrollX = TRUE,
  searchHighlight = TRUE,
  fixedColumns = list(leftColumns = 1)), rownames = FALSE)
```

# Liquidity

## Interest bearing liability  {.tabset}

Interest bearing liability is the sum of `r paste(with(meta_ts_fin_cuml, label_en[match(nam_var_interest_loan, varR)]), collapse = ', ')`.

### Cumulative YtD view

```{r warning = FALSE}
nam_var_2_plot <- nam_var_interest_loan
lst_res_2_show <- select(df_ts_fin_cuml, one_of(nam_var_date, nam_var_2_plot)) %>% 
  mutate_(.dots = set_names(paste(nam_var_2_plot, collapse = " + "), "int_bear_liab")) %>% 
  select(one_of(nam_var_date), int_bear_liab) %>% 
  arrange_(.dots = nam_var_date) %>% 
  cal_QoQ_YoY_of_df("int_bear_liab") %>% 
  filter_(.dots = paste0(nam_var_date, " %in% date_qtr_back")) %>% 
  plot_df_val_QoQ_YoY(data_frame(varR = "int_bear_liab", label = "Interest bearing liability"), nam_var_date)
plotly::ggplotly(lst_res_2_show$obj_ggplot)
```

```{r warning = FALSE}
DT::datatable(lst_res_2_show$df_view_ts, extensions = 'FixedColumns', options = list(
  pageLength = 3,
  scrollX = TRUE,
  searchHighlight = TRUE,
  fixedColumns = list(leftColumns = 1)), rownames = FALSE)
```



### Single Qtr 

```{r warning = FALSE}
nam_var_2_plot <- nam_var_interest_loan
lst_res_2_show <- select(df_ts_fin_single, one_of(nam_var_date, nam_var_2_plot)) %>% 
  mutate_(.dots = set_names(paste(nam_var_2_plot, collapse = " + "), "int_bear_liab")) %>% 
  select(one_of(nam_var_date), int_bear_liab) %>% 
  arrange_(.dots = nam_var_date) %>% 
  cal_QoQ_YoY_of_df("int_bear_liab") %>% 
  filter_(.dots = paste0(nam_var_date, " %in% date_qtr_back")) %>% 
  plot_df_val_QoQ_YoY(data_frame(varR = "int_bear_liab", label = "Interest bearing liability"), nam_var_date)
plotly::ggplotly(lst_res_2_show$obj_ggplot)
```

```{r warning = FALSE}
DT::datatable(lst_res_2_show$df_view_ts, extensions = 'FixedColumns', options = list(
  pageLength = 3,
  scrollX = TRUE,
  searchHighlight = TRUE,
  fixedColumns = list(leftColumns = 1)), rownames = FALSE)
```


# Inventory

## Inventory vs Operating Income {.tabset}

Pitfall: inventory growth outpace of operating income

<!-- Warning: high inventory with low gross profit might lead to inventory impairment (if downturn).  -->


### Cumulative YtD view

```{r warning = FALSE}
nam_var_2_plot <- c(nam_var_inventory, nam_var_op_income)
lst_res_2_show <- select(df_ts_fin_cuml, one_of(nam_var_date, nam_var_2_plot)) %>% 
  arrange_(.dots = nam_var_date) %>% 
  cal_QoQ_YoY_of_df(nam_var_2_plot) %>% 
  filter_(.dots = paste0(nam_var_date, " %in% date_qtr_back")) %>% 
  plot_df_val_QoQ_YoY(rename(select(meta_ts_fin_cuml, varR, label_en), label = label_en), nam_var_date)
plotly::ggplotly(lst_res_2_show$obj_ggplot)
```

```{r}
DT::datatable(lst_res_2_show$df_view_ts, extensions = 'FixedColumns', options = list(
  pageLength = 3,
  scrollX = TRUE,
  searchHighlight = TRUE,
  fixedColumns = list(leftColumns = 1)), rownames = FALSE)
```

### Single Qtr 

```{r warning = FALSE}
nam_var_2_plot <- c(nam_var_inventory, nam_var_op_income)
lst_res_2_show <- select(df_ts_fin_single, one_of(nam_var_date, nam_var_2_plot)) %>% 
  arrange_(.dots = nam_var_date) %>% 
  cal_QoQ_YoY_of_df(nam_var_2_plot) %>% 
  filter_(.dots = paste0(nam_var_date, " %in% date_qtr_back")) %>% 
  plot_df_val_QoQ_YoY(rename(select(meta_ts_fin_cuml, varR, label_en), label = label_en), nam_var_date)
plotly::ggplotly(lst_res_2_show$obj_ggplot)
```

```{r}
DT::datatable(lst_res_2_show$df_view_ts, extensions = 'FixedColumns', options = list(
  pageLength = 3,
  scrollX = TRUE,
  searchHighlight = TRUE,
  fixedColumns = list(leftColumns = 1)), rownames = FALSE)
```


## Inventory and Advance Receipts  {.tabset}

Potential: PnL management indicator. Deals might be finished, just book them in these accounts for near future income release. Check inventory details for confirmation.

### Cumulative YtD view

```{r warning = FALSE}
nam_var_2_plot <- c(nam_var_inventory, nam_var_advance_receipt)
lst_res_2_show <- select(df_ts_fin_cuml, one_of(nam_var_date, nam_var_2_plot)) %>% 
  arrange_(.dots = nam_var_date) %>% 
  cal_QoQ_YoY_of_df(nam_var_2_plot) %>% 
  filter_(.dots = paste0(nam_var_date, " %in% date_qtr_back")) %>% 
  plot_df_val_QoQ_YoY(rename(select(meta_ts_fin_cuml, varR, label_en), label = label_en), nam_var_date)
plotly::ggplotly(lst_res_2_show$obj_ggplot)
```

```{r}
DT::datatable(lst_res_2_show$df_view_ts, extensions = 'FixedColumns', options = list(
  pageLength = 3,
  scrollX = TRUE,
  searchHighlight = TRUE,
  fixedColumns = list(leftColumns = 1)), rownames = FALSE)
```

### Single Qtr 

```{r warning = FALSE}
nam_var_2_plot <- c(nam_var_inventory, nam_var_advance_receipt)
lst_res_2_show <- select(df_ts_fin_single, one_of(nam_var_date, nam_var_2_plot)) %>% 
  arrange_(.dots = nam_var_date) %>% 
  cal_QoQ_YoY_of_df(nam_var_2_plot) %>% 
  filter_(.dots = paste0(nam_var_date, " %in% date_qtr_back")) %>% 
  plot_df_val_QoQ_YoY(rename(select(meta_ts_fin_cuml, varR, label_en), label = label_en), nam_var_date)
plotly::ggplotly(lst_res_2_show$obj_ggplot)
```

```{r}
DT::datatable(lst_res_2_show$df_view_ts, extensions = 'FixedColumns', options = list(
  pageLength = 3,
  scrollX = TRUE,
  searchHighlight = TRUE,
  fixedColumns = list(leftColumns = 1)), rownames = FALSE)
```




## Inventory vs gross margin

##



